Discovering cell type motifs in connectomics data

### 2013-12-11 docs/paper.tex
Latest version of text

\begin{abstract}
  New techniques produce massive data about neural connectivity,
  necessitating new analysis methods to discover underlying
  structure. There is strong evidence for microcircuitry, where the
  probability of connections depends on the types of pre- and
  post-synaptic neurons and their distance. Here we developed a
  nonparametric Bayesian technique that identifies neuron type and circuitry
  patterns from the connection data. We show that the approach recovers
  known neuron types in the retina, reveals interesting structure in
  the nervous system of c. elegans, and automatically discovers the
  structure of microprocessors. Our approach is a first step towards
  condensing connectomics data into meaningful, human readable
  structure.
\end{abstract}

\section*{Introduction}
Emerging techniques \autocite{Lichtman, Zador, Denk} promise to
quantify the location of each neuron within a volume of interest,
along with its connections to all other neurons. Far exceeding the
capacity of neuroanatomists to trace small circuits, this leads to
enormous datasets that quantify aspects of the nervous system. The
rise of high-throughput sequencing techniques necessitated the
development of novel computational methods to understand genomic
structure, ushering in an era of bioinformatics as an independent
discipline \autocite{}.

@@

The discovery of structure is a crucial aspect of network
science. Early approaches focused on global graph properties, such as
the types of scaling present in the network \autocite
{WattsStrogatz1998} .  While this approach leads to an understanding
of global network, more recent work aims at identifying small-scale
repeat patterns, or “motifs” in networks. \todo{There's the
  Science2002 paper by Milo et. al. that explicitly looks at 'motifs'}
A motif is a set of nodes with conserved relations that appears
multiple times in a network, for example a set of three nodes that are
each connected to one another.

When it comes to neuroscience, we might
expect that a motif consists of the kinds of cells that jointly make
up a microcircuit along with their distance and cell-type dependent
connectivity. The same motif should then appear in multiple locations
in the nervous system. Combining motif-discovery ideas with specific
knowledge about the kinds of motifs in the nervous system promises
better structure discovery.

@@

Here we describe a Bayesian non-parametric model that can discover
circuit structure automatically from connectomics data: both the cell
types and their spatial patterns of interconnection. We apply it to
three computing systems: the mouse retina connectome \autocite{}, the
c. elegans connectome \autocite{}, and a ``connectome'' of a classical
microprocessor. In all cases, we discover cell-type to cell-type
connectivity that depends on spatial distance and these connectivity
functions depend on the two involved cell types. Comparing the cell
types discovered by the algorithms with those obtained by anatomists
based on orthogonal information reveals a high degree of agreement. We
present a scalable approach to infer microcircuitry from connectivity
data.

@@

\section{Results}
We use a Bayesian structure discovery approach that is based on
assumptions about the way positions and cell types affect the
probability of connections between cells, a so-called generative
model. The probability of connections between pairs of neurons
decreases with distance, but how high the baseline probability of
connection is and how quickly it decays with distance depends on the
two cell-types. We combine annealing with Markov Chain Monte Carlo to
perform simultaneously joint posterior inference over the structure,
parameters, and hyperparameters of the model. This procedure yields a
division of all neurons into cell-types along with the distance and
type dependent connectivity probabilities. These results can then be
compared with the results of previous anatomical studies that have
used other aspects of neurons, such as chemical properties and
cell-morphology to divide neurons into types.

@@

The roundworm Caenorhabditis elegans is a model system in
developmental neuroscience\autocite{White1986}, with the location and
connectivity of each of 302 neurons deterministically known. This
incredible cross-organism consistency led to early mapping of the
c. elegans chemical and electrical (gap junction) connectome. Unlike
the retina, only the motor neurons in c. elegans exhibit regular
distribution in space, as they follow the body axis. Most interneurons
are concentrated in various ganglia that project throughout the entire
animal, and the sensory neurons are primarily located in the animal
head.

Using both the chemical and electrical connectivity (see methods), we
determined the underlying clusters explained by connectivity and
distance (fig ba). A superficial inspection of the results shows
clustering into groups consisting roughly homogeneously of motor
neurons, sensory neurons, and interneurons. Closer examination reveals
agreement with the classifications originally outlined by Brenner in
1986.  [create structure that mirrors the mouse retina paragraphs]

[start paragraph with summary sentence] Motorneuron types AS, DA, and
VA, all exclusively postsynaptic, are clustered together, as are
motorneuron types VD and DD. VC, DB, and VB also mostly share a
cluster. Various head motor neurons, including classes SMD, RMD, and
RIM are clustered together. Interneurons with known
anatomically-distinct connectivity patterns, such as RIA (2 cells) or
AVA (2 cells) are clustered into pure groups. The algorithm even
correctly places the single-cell class DVB in a distinct group. Note
our clustering does not perfectly recover known groupings -- several
combinations of head and sensory neurons are combined, and a
difficult-to-explain group of 2 VD, 2 VB, a VA, and a DD neuron are
grouped together. [algorithm recovers surprising structure based
merely on connectivity even though only 278 cells and not spatially
homogeneous]

@@

To show the applicability of our method to other connectome-style
datasets, we obtained the spatial location and interconnectivity of a
transistors in a classic microprocessor, the MOS Technology 6502 (used
in the Apple II) \autocite{datasource}. We identified a region of the
processor with complex but known structure containing the primary
general-purpose registers X, Y, and S (figure). Computer architects
use common patterns of transistors when designing circuits, 
with each transistor having a ``type'' in the circuit.

Our algorithm identifies areas of spatial homogeneity that mirror the
kown structure in the underlying architectural circuit, segementing
transistor groups. One group contains the ``clocked'' transistors,
one group with their source connected to ground, and one with their
drain connected to ground. The repeat patterns of spatial connectivity
are visible in figure~\ref{fig:microprocessor}a,

@@

\section{Discussion}
We have presented a machine learning technique that allows cell types
and connectivity structure to be discovered using only spatial and
connectivity data. We have shown its applicability to a newly
published connectomics dataset from the mouse retina, the classical
connectivity of the worm c elegans, and the connectivity of a
historical man-made microprocessor. We have found that spatial
connectivity alone is sufficient to discover interesting motifs that
were known to exist in the systems based on decades of previous
research which had utilized extensive additional information. “

@@

Our inference becomes slower as the amount of data increases. Our
algorithm required 10xxx hours for 1000 neurons and would therefore
take months for 10,000 neurons, which would not be acceptable. Various
new techniques promise to allow similar calculations to take less time
and scale to larger datasets \autocite{}.

*Fixed and hand selected likelihood link functions We picked the
sigmoid. Should be estimated, Our small collection of parametric forms
for spatial functions are obviously not exhaustive

*We do not use other sources of information that are totally there in
the datasets. Cell morphology could be used. Laminar organization.

*Larger datasets will generally allow algorithms to distinguish more
distinct types (cite supplemental data) and more data should
algorithms to get closer to the results from anatomy. Moreover, in
general, for such problems precision increases with the size of the
dataset and the 9xxx cells that we have are not sufficient to
statistically distinguish all the cell types known in anatomy
(71xxx). Still, using only connectivity it is possible to meaningfully
divide neurons into classes.

[ how this changes things] There exist a range of previous approaches
to the discovery of microcircuitry [coherence of language]
(cites). These generally involve a great deal of manual labor and
ad-hoc determination of what constitutes a “type” of cell -- to this
day there are disagreements in the literature as to the “true” types
in the mammalian retina. Much as phylogenomics has changed our
understanding of animal ontologies, modern large scale data will allow
the efficient unbiased discovery of structure. The sheer amount of
available data demands the introduction of algorithmic approaches.

*A new way of phenotyping, combining spatial motif ideas with clustering ideas

*Novel data analysis techniques are required to lead us into the big
data age. Our approach is orthogonal to all others (because in high d
everything is orthogonal).

@@

We assume as input a connectivity matrix $R$ defining the connections
between cells, as well as a distance function $d(e_i, e_j)$
representing a (physical) distance between adjacent cells. See the
supplemental material for extension to multiple connectivity
matrices. We assume there exist an unknown number of latent
(unobserved) cell types, $k$, $k \in \{1, 2, 3, \dots\}$, and that
each cell $e_i$ belongs to a single cell type, $c_i = k$. The observed
connectivity between two cells $R(e_i, e_j)$ then only depends on
their latent type and their distance through a link function $f(c_i,
c_j, d(e_i, e_j))$ If $c_i=m$ and $c_j=n$ then there exists a
latent-class-specific set of parameters $\eta_{mn}$ which parametrizes
$f$, as well as a set of global hyper parameters $\theta$.

We then jointly compute the maximum a posteriroi (MAP) estimate of the
class assignment vector ${c_i}$, the parameter matrix $\eta_{mn}$, and
the global model hyperparameters $\theta$ :

@@

We describe three link functions, ``Logistic-distance Bernoulli'',
``logistic-distance fixed-lambda Bernoulli'', and ``logistid-Distance
Poisson''.

The ``logistic-distance Bernoulli'' model associates with each latent class 
two parameters, $\mu_{mn}$ and $\lambda_{mn}$, and the probability that two
cells $e_i$ and $e_j$ are connected is given by
\begin{eqnarray}
p^* &=& \frac{1.0}{1 + \exp \frac{d(e_i, e_j) - \mu_{mn}}{\lambda_{mn}}}\\
p &= & p^* \cdot (p_{max} - p_{min}) + p_{min}
\end{eqnarray}
where $p_{max}$ and $p_{min}$ are per-graph hyperparameters. Per-component parameters $\mu_{mn} \sim \exp(\mu | \mu^{hp})$ and $\lambda_{mn} \sim \exp(\lambda | \lambda^{hp})$. 
Inference is performed on these hyperparameters as well, see TODO supplemental 
for details.

@@

\subsection {Mouse Retina}
Dense serial electron microscopy of a $VOLUMNE$ in the mouse retina by
\autocite{Helmstaedter2013} yielded a listing of places where neurons
come into contact. There were $number$ cells originally, and selected
the $950$ for which the location of the soma could be reconstruted
from the provided cell plots (soma locations were not provided by the
study's authors in machine-readble form). Ultimately
this left a matrix between the total synapse-like contact area between
all pairs of 950 cells. Area was thresholded at $0.5\mu m$, determined
by hand, to yield a 950 $\times$ 950 entry matrix that served as input
to our algorithm. We measured the distance between cells using
the reconstructed soma centers, and used the Logistic-Distance
spatial relation. Hyperprior distributions are shown in \ref{supplemental}.

@@

We obtained the connectome of c. elegans from \autocite, and isolated
the 279 nonpharyngeal neurons, with a total of 6393 chemical synapses
and 890 gap junctions originally cleaned up in \autocite{Chen2006}. A
cell's position was its distance along the anterior-posterior axis
normalzed between zero and one. We used both networks, the chemical
network as a directed graph and the electrical network as undirected
graph. We use the synapse counts with the logistic-distance poisson
likelihood, scaling the counts by a factor of 4 to compensate for 
the Poisson's overdispersion.

\subsection{Microprocessor}
We extracted the connection graph for all transistors in the MOS6502
\autocite{visual6502}. Each transistor has three terminals: an input
G, a source, and a drain, labeled C1 and C2. We identified the region
consisting of the three general-purpose registers X, Y, and S via
visual inspection and focused our efforts there. We created a total of
six connectivity matrices by examining possible terminal parings. One
graph, for example, $R^{gc_1}(e_i, e_j)=1$ if transistor $e_j$ and $e_j$ are
connected via pins $g$ and $c_1$. 
\todo{How do we handle symmetry here?}

@@

\subsection{Extension to multiple graphs}
The model can handle multiple graphs $R^q$ simultaneously with a shared clustering by simply considering the product of 
\begin{equation}
  p(\vec{c}, \{\eta^q\}, \{\theta^q\} | \{R^q\} ) \propto \prod_q \Bigg(\prod_{i, j} p(R^q(e_i, e_j) | f(d(e_i, e_j) | \eta^q_{c_ic_j}), \theta^q) \prod_{m, n} p(\eta^q_{mn} | \theta^q)  p(\theta^q) \Bigg) p(\vec{c} | \alpha) p(\alpha) 
\end{equation}

\subsection{Microprocessor Netlist annotation}
\begin{figure}
  \centering 
    \centerline{\includegraphics[width=183mm]{mos6502/sixrelation.xysregs.ldfl.circos.4.R2.ai}}
\end{figure}

@@

For the mouse retina Logistic-Distance Bernoulli model, we gridded $\mu^{hp}$ and $\lambda^{hp}$ into 40 $\log_{10}$-spaced points 1.0 and 80. $p_{min} \in [0.001, 0.005, 0.01]$ and $p_{max} \in [0.80, 0.90, 0.95, 0.99$.

For the c. elegans data with the Logistic Distance poisson model, we gridded $\mu_{hp$ and $\lambda$ into 20 $\log_{10}$-spaced points bween 0.2 and 2.0, and the $ratescale^{hp}$ parameter into 20 $\log_{10}$-spaced points between 2.0 and 20.0. We globally set $rate_{min}=0.01$.

>>>>

\begin{abstract}
  New techniques produce massive data about neural connectivity,
  necessitating new analysis methods to discover underlying
  structure. There is strong evidence for microcircuitry, where the
  probability of connections depends on the types of pre- and
  post-synaptic neurons and their distance. Here we developed a
  nonparametric Bayesian technique that identifies neuron type and circuitry
  patterns using only this connection data. We show that the approach recovers
  known neuron types in the retina, reveals interesting structure in
  the nervous system of c. elegans, and automatically discovers the
  structure of microprocessors. Our approach is a first step towards
  condensing connectomics data into meaningful, human readable
  structure.
\end{abstract}

\section*{Introduction}
Emerging techniques \autocite{Lichtman, Zador, Denk} promise to
quantify the location of each neuron within a volume of interest,
along with its connections to all other neurons. Far exceeding the
capacity of neuroanatomists to trace small circuits, this leads to
enormous datasets that quantify aspects of the nervous system. The impact of
this kind of high-throughput transition has been seen before -- 
rise of sequencing techniques necessitated the
development of novel computational methods to understand genomic
structure, ushering in an era of bioinformatics as an independent
discipline \autocite{}.

@@

The discovery of structure is a crucial aspect of network
science. Early approaches focused on global graph properties, such as
the types of scaling present in the network \autocite
{WattsStrogatz1998} .  While this approach leads to an understanding
of global network, more recent work aims at identifying very small-scale
repeat patterns, or “motifs” in networks\autocite{Milo2002}

@@

When it comes to neuroscience and other computing systems, we expect
patterns of connectivity much more compelx than traditional motifs,
exhibiting a strong spatial dependence arising from the complex
genetic, chemical, and activity-based neural development process.

Here we describe a Bayesian non-parametric model that can discover
circuit structure automatically from connectomics data: both the cell
types and their spatial patterns of interconnection. We apply it to
three computing systems: the mouse retina connectome \autocite{}, the
c. elegans connectome \autocite{}, and a ``connectome'' of a classical
microprocessor. Note we do not explicitly consider cellular
morphology, absolute position (cell layer), or any chemical or genetic
information. Yet in all cases, we discover cell-type to cell-type
connectivity that depends on spatial distance and these connectivity
functions depend on the two involved cell types. Comparing the cell
types discovered by the algorithms with those obtained by anatomists
based on orthogonal information reveals a high degree of agreement. We
present a scalable approach to infer microcircuitry from connectivity
data.

@@

\section{Results}
We use a Bayesian structure discovery approach that is based on
assumptions about the way positions and cell types affect the
probability of connections between cells, a so-called generative
model. The probability of connections between pairs of neurons
decreases with distance, but how high the baseline probability of
connection is and how quickly it decays with distance depends on the
two cell-types. We combine annealing with Markov Chain Monte Carlo to
perform simultaneously joint posterior inference over the structure,
parameters, and hyperparameters of the model (see Methods). This
procedure yields a division of all neurons into cell-types along with
the distance and type dependent connectivity probabilities. These
results can then be compared with the results of previous anatomical
studies that have used other aspects of neurons, such as chemical
properties and cell-morphology to divide neurons into types.

@@

The roundworm Caenorhabditis elegans is a model system in
developmental neuroscience\autocite{White1986}, with the location and
connectivity of each of 302 neurons deterministically known. This
incredible cross-organism consistency led to early mapping of the
c. elegans chemical and electrical (gap junction) connectome. Unlike
the retina, only the motor neurons in c. elegans exhibit regular
distribution in space, being distributed along the body axis. Most
interneurons are concentrated in various ganglia that project
throughout the entire animal, and the sensory neurons are primarily
located in a small number of very anteriior ganglia.

Using both the chemical and electrical connectivity (see methods), we
determined the underlying clusters explained by connectivity and
distance (fig ba). A superficial inspection of the results shows
clustering into groups consisting roughly homogeneously of motor
neurons, sensory neurons, and interneurons. Closer examination reveals
agreement with the classifications originally outlined by Brenner in
1986.

We identify cell types that reflect the known motor/non-motor neuron
classes, even though this system lacks the strong repeat
microcircuitry our model was designed for.  Motorneuron types AS, DA,
and VA, all exclusively postsynaptic, are clustered together, as are
motorneuron types VD and DD. Traditional types VC, DB, and VB also
mostly share a cluster. Various head motor neurons, including types
SMD, RMD, and RIM are clustered together. Interneurons with known
anatomically-distinct connectivity patterns, such as RIA (2 cells) or
AVA (2 cells) are clustered into pure types. The algorithm even
correctly places the single-cell type DVB by itself. Note our
clustering does not perfectly reflect known divisions -- several
combinations of head and sensory neurons are combined, and a
difficult-to-explain group of 2 VD, 2 VB, a VA, and a DD neuron are
grouped together. Our identified cell types thus reflect a
``coarsening'' of known types, based entirely on connectivity and
distance information, evne when the organism exhibits substantially
less spatial regularity than the retina.

@@

To show the applicability of our method to other connectome-style
datasets, we obtained the spatial location and interconnectivity of
the transistors in a classic microprocessor, the MOS Technology 6502
(used in the Apple II) \autocite{datasource}. Computer architects use
common patterns of transistors when designing circuits, with each
transistor having a ``type'' in the circuit. We identified a region of
the processor with complex but known structure containing the primary
8-bit registers X, Y, and S (figure).

Our algorithm identifies areas of spatial homogeneity that mirror the
known structure in the underlying architectural circuit, segementing
transistor types recognizable to computer architects. Using the
original schematics, we see that one identified type contains the
``clocked'' transistors, which retain digital state. Two other types
contain transistors with pins C1 or C2 connected to ground, mostly
serving as inverters.  An additional identified type controls the
behavior of the three registers of interest (X, Y, and S) with respect
to the SB data bus, either allowing them to latch or drive data from
the bus. The repeat patterns of spatial connectivity are visible in
figure~\ref{fig:microprocessor}a, showing the man-made horizontal and
vertical layout of the same types of transistors.

@@

\section{Discussion}
We have presented a machine learning technique that allows cell types
and microcircuitry to be discovered using only distance and
connectivity data. We have shown its applicability to a newly
published connectomics dataset from the mouse retina, the classical
connectivity of the worm c. elegans, and the connectivity of a
historical man-made microprocessor. We have found that distance and
connectivity alone are sufficient to discover cell types and
microcircuitry that were known to exist in the systems based on decades
of previous research which had utilized extensive additional
information.

@@

Our inference becomes slower as the amount of data increases. Our
algorithm required 30 hours for 1000 neurons and could take months for
substantially longer datasets. Scaling this class of probabilistic
model is an active area of research, and recent results in both
variational methods \autocite{Hoffmann2013} and spectral learning
  \autocite{Anandkumar2012} promise substantial speed increases.

  Larger datasets will generally allow algorithms to distinguish more
  distinct types (cite supplemental data) and more data should
  algorithms to get closer to the results from anatomy. Moreover, in
  general, for such problems precision increases with the size of the
  dataset and the cells that we have are not sufficient to
  statistically distinguish all the cell types known in anatomy
  (71xxx). Still, using only connectivity and distance it is possible
  to meaningfully divide neurons into types.

Our small collection of hand-selected distance-dependent likelihood
functions are clearly non-exhaustive, and assume monotonicity
of connectivity probability -- for a given class, closer cells
are never less-likely to connect. This is known to be insufficient
for various neural systems. Future models could incorporate
a wider variety of likelihood functions, or even learn the global
functional form from the data.

There have existed a a range of previous approaches to the discovery
of neural microcircuitry (cites). These generally involve a great deal
of manual labor and ad-hoc determination of what constitutes a “type”
of cell -- to this day there are disagreements in the literature as to
the “true” types in the mammalian retina. Much as phylogenomics has
changed our understanding of animal ontologies, modern large scale
data will allow the efficient unbiased discovery of cell types and
circuits. The sheer amount of available data demands the introduction
of algorithmic approaches.

The development of automatic identification and quantification of cell
type may also provide new phenotypic tools for quantifying the effect
of disease, genetic abnormalities, and genetic
interventions. Particular pathologies and genetic manipulations may
subtly change the number and connectivity of cell types in ways
only visible with algorithmic analysis.

@@

We take as input a connectivity matrix $R$ defining the connections
between cell $e_i$ and $e_j$, as well as a distance function $d(e_i, e_j)$
representing a (physical) distance between adjacent cells. See the
supplemental material for extension to multiple connectivity
matrices. We assume there exist an unknown number $k$ of latent
(unobserved) cell types, $k \in \{1, 2, 3, \dots\}$, and that
each cell $e_i$ belongs to a single cell type, $c_i = k$. The observed
connectivity between two cells $R(e_i, e_j)$ then depends only on
their latent type and their distance through a link function $f(\cdot, d(e_i, e_j))$. We assume $f$ is parameterized based on the latent class, $c_i=m$ and $c_j=n$, via a parameter$\eta_{mn}$, as well as a set of global hyper parameters $\theta$, such that the link function is $f(d(e_i, e_j) | \eta_{mn}, \theta)$.

We then jointly infer the maximum a posteriroi (MAP) estimate of the
class assignment vector ${c_i}$, the parameter matrix $\eta_{mn}$, and
the global model hyperparameters $\theta$ :

@@

We describe three link functions, ``Logistic-distance Bernoulli'',
``logistic-distance fixed-lambda Bernoulli'', and ``logistic-Distance
Poisson''.

% fixme class component, NOT class
The ``logistic-distance Bernoulli'' link model assumes that, if cell
$e_i$ is of class $m$ and cell $e_j$ is of class $n$, then $\eta_{mn}
= (\mu_{mn}, \lambda_{mn})$, and the probability that two cells $e_i$
and $e_j$ are connected is given by
\begin{eqnarray}
p^* &=& \frac{1.0}{1 + \exp \frac{d(e_i, e_j) - \mu_{mn}}{\lambda_{mn}}}\\
p &= & p^* \cdot (p_{max} - p_{min}) + p_{min}
\end{eqnarray}
where $p_{max}$ and $p_{min}$ are per-graph hyperparameters. Per-component parameters $\mu_{mn} \sim \exp(\mu | \mu^{hp})$ and $\lambda_{mn} \sim \exp(\lambda | \lambda^{hp})$.

@@

\subsection {Mouse Retina}
Dense serial electron microscopy of a $VOLUMNE$ in the mouse retina by
\autocite{Helmstaedter2013} yielded a listing of places where neurons
come into contact. There were over 1000 cells originally, and selected
the $950$ for which the location of the soma could be reconstruted
from the provided cell plots (soma locations were not provided by the
study's authors in machine-readble form). Ultimately
this left a matrix between the total synapse-like contact area between
all pairs of 950 cells. Area was thresholded at $0.5\mu m$, determined
by hand, to yield a 950 $\times$ 950 entry matrix that served as input
to our algorithm. We measured the distance between cells using
the reconstructed soma centers, and used the Logistic-Distance
spatial relation. Hyperprior griddings are shown in \ref{supplemental}.

@@

We obtained the connectome of c. elegans from \autocite, and isolated
the 279 nonpharyngeal neurons, with a total of 6393 chemical synapses
and 890 gap junctions originally cleaned up in \autocite{Chen2006}. A
cell's position was its distance along the anterior-posterior axis
normalzed between zero and one. We used both networks, the chemical
network as a directed graph and the electrical network as undirected
graph. We use the synapse counts with the logistic-distance poisson
likelihood, scaling the counts by 4.0 to compensate for 
the Poisson's overdispersion.

\subsection{Microprocessor}
We extracted the connection graph for the transistors in the MOS6502
\autocite{visual6502}. Each transistor has three terminals (gate,
source, drain), but the methods of the original dataset were unable to
consistently resolve which of the C1 and C2 terminals were source and
drain, leading to ambiguity in our encoding. We identified a region
consisting of consisting of three registers X, Y, and S via visual
inspection and focused our efforts there. We created a total of six
connectivity matrices by examining possible terminal parings. One
graph, for example, $R^{gc_1}(e_i, e_j)=1$ if transistor $e_j$ and
$e_j$ are connected via pins $g$ and $c_1$.

@@

\subsection{Extension to multiple graphs}
The model can handle multiple graphs $R^q$ simultaneously with a shared clustering by simply considering the product of 
\begin{equation}
  p(\vec{c}, \{\eta^q\}, \{\theta^q\} | \{R^q\} ) \propto \prod_q \Bigg(\prod_{i, j} p(R^q(e_i, e_j) | f(d(e_i, e_j) | \eta^q_{c_ic_j}, \theta^q) \prod_{m, n} p(\eta^q_{mn} | \theta^q)  p(\theta^q) \Bigg) p(\vec{c} | \alpha) p(\alpha) 
\end{equation}

\subsection{Microprocessor Netlist annotation}
This is a matrix consisting of the different clusters of nets for 
the registers.

@@

For the mouse retina Logistic-Distance Bernoulli model, we gridded $\mu^{hp}$ and $\lambda^{hp}$ into 40 $\log_{10}$-spaced points 1.0 and 80. $p_{min} \in [0.001, 0.005, 0.01]$ and $p_{max} \in [0.80, 0.90, 0.95, 0.99]$.

For the c. elegans data with the Logistic Distance poisson model, we gridded $\mu_{hp}$ and $\lambda$ into 20 $\log_{10}$-spaced points bween 0.2 and 2.0, and the $ratescale^{hp}$ parameter into 20 $\log_{10}$-spaced points between 2.0 and 20.0. We globally set $rate_{min}=0.01$.

For the microprocessor with the Logistic Distance fixed lambda Bernoulli likelihood, we gridded $mu_{hp}$ into 50 $\log_{10}$-spaced points between 10 and 500 and set $\lambda=\mu_{hp}/10$. $p_{min} \in \{0.001, 0.01, 0.02\}$  and both $p_\alpha$ and $p_\beta \in \{0.1, 1.0, 2.0\}$.
